Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-23 paper/paper.tex
pass on approach

\tname{} is a search-based approach that uses positive and negative
network traffic examples to synthesize signature-based NIDS rules,
such as those from Snort and Suricata. \tname{} synthesizes rules in
two steps. First, it produces a potentially overspecified rule that
captures the negative example that is provided as input. Then, it uses
positive examples to eliminate unnecessary options from the rule. The
goal of \tname\ is to create a rule that captures only the negative traffic.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[trim=60 400 65 0,clip,width=0.7\textwidth]{figs/nids-workflow}
\caption{\tname workflow. The first step initializes the encoding of
  randomly initializes the rule encoding. Only options associated with
  the protocol usd in the negative traffic are included in the
  encoding. This step mutates the values associated with rule options
  until \suri\ is able to capture the attack.  Note that any subset of
  options in the rule reported in this step captures the negative
  traffic. The second step is initialized with a configuration that
  captures the negative traffic but could also capture benign
  traffic. It discards options from the rule encoding until no
  positive traffic is captured.}
\label{fig:overview}
\end{figure*}

\tname{} is a search-based approach that uses positive and negative
network traffic examples to synthesize signature-based NIDS rules,
such as those from Snort and Suricata.

Figure~\ref{fig:overview} shows the workflow of \tname{}.  The
technique synthesizes rules in two steps. First, it produces a
potentially overspecified rule that captures the negative example that
is provided as input. Then, it uses positive examples to eliminate
unnecessary options from the rule. The goal of \tname\ is to create a
rule that only captures the negative traffic.

\Fix{describes negative and positive traffic}
